---
title: "Adaboost"
author: "Felipe González"
date: Otoño 2015
output: 
  html_document: 
    theme: united
---


```{r, warning=FALSE, message=FALSE}
library(rpart)
library(dplyr)
library(tidyr)
library(ggplot2)
```

### Datos

 The file "sonar.mines" contains 111 patterns obtained by bouncing sonar 
signals off a metal cylinder at various angles and under various conditions. 
The file "sonar.rocks" contains 97 patterns obtained from rocks under similar
conditions. The transmitted sonar signal is a frequency-modulated chirp, 
rising in frequency. The data set contains signals obtained from a variety 
of different aspect angles, spanning 90 degrees for the cylinder and 180 degrees for the rock.
 
 Each pattern is a set of 60 numbers in the range 0.0 to 1.0. 
 Each number represents the energy within a particular frequency band, 
 integrated over a certain period of time. The integration aperture for higher 
 frequencies occur later in time, since these frequencies are transmitted later during the chirp.
 
 The label associated with each record contains the letter "R" if 
 the object is a rock and "M" if it is a mine (metal cylinder). The numbers 
 in the labels are in increasing order of aspect angle, but they do not encode 
 the angle directly.
 
```{r}
sonar_entrena <- read.table("datos/sonar_train.csv",sep=",")
sonar_prueba <- read.table("datos/sonar_test.csv",sep=",")
table(sonar_entrena$V61)

table(sonar_prueba$V61)

sonar_entrena_1 <- sonar_entrena
sonar_entrena_1$id <- 1:nrow(sonar_entrena)
sonar_m <- sonar_entrena_1 %>% gather(vars, valor, V1:V60)
ggplot(sonar_m, aes(x=vars, y=valor, colour=factor(V61), group=id))+
   geom_line()
 
```